Voting Patterns and Socio-Economic Tides: A Twenty-Year Analysis of Brazil's Developmental Dynamics

### 2024-02-13 outputs/paper/paper.qmd
final version of paper.qmd

---
title: "Voting Patterns and Socio-Economic Tides: A Twenty-Year Analysis of Brazil's Developmental Dynamics"
author: "Hao Wang / Siqi Fei / Xuecheng Gao"
thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: www.aeaweb.org/articles?id=10.1257/app.20210529"
date: "February 12, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: " "
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes 
nocite: '@*'
bibliography: references.bib
---

@@

data_path <- here("outputs", "edited_data", "election_cleaned.csv")
election <- read.csv(data_path)
data_path2 <- here("outputs", "edited_data", "schools.csv")
school <- read.csv(data_path2)
```
\newpage
\begin{center}
\textbf{\large Abstract}
\end{center}

@@

-   **Indicators Included**:

    -   `cut_dist`: A geographical identifier for districts or electoral cuts, offering spatial analysis opportunities.
    -   `elect_year`: The year of the election, anchoring the socio-economic data within a political timeline.
    -   `inc_post`: Per capita income figures post-election, reflecting the general economic well-being.
    -   `inc_0_50_post`: Income figures for the bottom 50% post-election, highlighting the economic status of the less affluent demographic.
    -   `edu_univ`: A variable intended to capture educational attainment or resources, yet unspecified in the initial data extract.
    -   `unempl_post`: Post-election unemployment rates, indicating labor market conditions.
    -   `tse_code`: Potentially linked to electoral zones or districts, allowing for analysis of electoral influence on socio-economic aspects.

@@

## Overview
```{r}
#| label: fig-hist
#| fig-cap: histogram
#| echo: false
#| message: false
#| warning: false
#| fig.width: 8
#| fig.height: 7

@@

## Ethical Implications

>>>>

---
title: "Voting Patterns and Socio-Economic Tides: A Twenty-Year Analysis of Brazil's Developmental Dynamics"
author: "Hao Wang / Siqi Fei / Xuecheng Gao"
thanks: "Code and data are available at: https://github.com/groundUofT888/Term-Paper-2.git ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qxvj-fz21"
date: "February 12, 2024"
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1in
    abstract: " "
    number-sections: true
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes 
nocite: '@*'
bibliography: references.bib
---

@@

data_path <- here("outputs", "edited_data", "election_cleaned.csv")
election <- read.csv(data_path)
data_path2 <- here("outputs", "edited_data", "schools.csv")
school <- read.csv(data_path2)
```

\begin{center}
\textbf{\large Abstract}
\end{center}

@@

-   **Indicators Included**:
    -   `cut_dist`: A geographical identifier for districts or electoral cuts, offering spatial analysis opportunities.
    -   `elect_year`: The year of the election, anchoring the socio-economic data within a political timeline.
    -   `inc_post`: Per capita income figures post-election, reflecting the general economic well-being.
    -   `inc_0_50_post`: Income figures for the bottom 50% post-election, highlighting the economic status of the less affluent demographic.
    -   `edu_univ`: A variable intended to capture educational attainment or resources, yet unspecified in the initial data extract.
    -   `unempl_post`: Post-election unemployment rates, indicating labor market conditions.
    -   `tse_code`: Potentially linked to electoral zones or districts, allowing for analysis of electoral influence on socio-economic aspects.

@@

## Overview
```{r}
#| label: fig-hist
#| fig-cap: "overview histogram"
#| echo: false
#| message: false
#| warning: false
#| fig.width: 8
#| fig.height: 7

@@

\newpage
## Ethical Implications
